Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/introduction.tex

Our goal is to automatically detect split and merge errors to reduce visual
inspection time. Further, to reduce correction time, we propose
corrections to the user to accept or reject. We call this process \textit{guided
proofreading}.

We learn a classifier for split errors with a convolutional neural network
(CNN). This takes as input patches of membrane segmentation probabilities, cell
segmentation masks, and boundary masks, and outputs a probability score. As we
must process large data, this classifier only operates on cell boundaries, which
reduces computation over methods that analyze every pixel. For merge errors, we
invert and reuse the split classification network, instead asking it to rate a
set of generated candidate boundaries that hypothesize a split. %We compute
%corrections for both types of errors.

We also propose a greedy algorithm for guided proofreading. Possible erroneous
regions are sorted by their score, and a candidate correction is generated for each
region. Then, a user works through this list of regions and corrections. In a
forced choice setting, the user either selects a correction or skips it to
advance to the next region. In an automatic setting, errors with a high
probability are automatically corrected first, given an appropriate
probability threshold, after which the user would take over. Finally, to test
the limits of performance, we create an oracle which only accepts corrections
that improve the segmentation, based on knowledge of the ground truth. This is
guided proofreading with a perfect user.

>>>>

Our goal is to automatically detect potential split and merge errors to reduce visual
inspection time. Further, to reduce correction time, we propose
corrections to the user to accept or reject. We call this process \textit{guided
proofreading}.

We train a classifier for split error detection with a convolutional neural network
(CNN). This takes as input patches of membrane segmentation probabilities, cell
segmentation masks, and boundary masks, and outputs a split-probability score. As we
must process large data, this classifier only operates on cell boundaries, which
reduces computation over methods that analyze every pixel. For merge errors, we
invert and reuse the split classification network, instead asking it to rate a
set of generated boundaries that hypothesize a split. %We compute
%corrections for both types of errors.

Possible erroneous regions are sorted by their score, and a candidate correction is generated for each
region. Then, a user works through this list of regions and corrections. In a
forced choice setting, the user either selects a correction or skips it to
advance to the next region. In an automatic setting, errors with a high probability are automatically corrected first, given an appropriate
probability threshold, after which the user would take over. Finally, to test
the limits of performance, we create an oracle which only accepts corrections
that improve the segmentation, based on knowledge of the ground truth. This is
guided proofreading with a perfect user.

### 2016-11-15 paper/method.tex
Add updated graphics.

\paragraph{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process by using a $75\times75$ pixel patch at the center of an existing boundary. This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset. If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary, and combine the resulting score by averaging weighted by the boundary length coverage per patch.

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/merge_error.pdf}
\end{center}
%  \vspace{-4mm}
   \caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

@@

We use the proposed classifiers in combination to perform corrections of split and merge errors in automatic segmentations. For this, we first perform merge error detection for all existing segments in a dataset and store the inverted rankings $1-p$ as well as potential corrections. After that, we perform split error detection and store the ranking $p$ for all neighboring segments in the segmentation. Then, we sort the merge and split error rankings separately from highest to lowest. For error correction, first we loop through the potential merge error regions and then through the potential split error regions. During this process, each error is now subject to a yes/no decision which can be provided in different ways:

\paragraph{Selection oracle.} If ground truth data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation. This is realized by simply comparing the outcome of a correction using a defined measure. The oracle only accepts corrections which improve the automatic segmentation---others get
discarded. This is guided proofreading with a perfect user, and allows us to assess the upper limit of performance.

@@

\paragraph{Forced choice setting.} We present a user with the choice to accept or reject a correction. All potential split errors are seen. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. Therefore, we only present merge errors that satisfy $1-p_t$.

@@

We integrate guided proofreading into an existing large data connectomics workflow. The web-based system is designed with a novice-friendly user interface (Fig.~\ref{fig:ui}). We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data. The user is not possible to distinguish the current labeling from the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown.

>>>>

\paragraph{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process by using a $75\times75$ pixel patch at the center of an existing boundary. This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset\footnote{\scriptsize{\url{http://openconnectomeproject.org/}}}. If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary, and average the resulting scores weighted by the boundary length coverage per patch.

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
\end{center}
%  \vspace{-4mm}
   \caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

@@

We combine the proposed classifiers to perform corrections of split and merge errors in automatic segmentations. For this, we first perform merge error detection for all existing segments in a dataset and store the inverted rankings $1-p$ as well as potential corrections. After that, we perform split error detection and store the ranking $p$ for all neighboring segments in the segmentation. Then, we sort the merge and split error rankings separately from highest to lowest. For error correction, first we loop through the potential merge error regions and then through the potential split error regions. During this process, each error is now subject to a yes/no decision which can be provided in different ways:

\paragraph{Selection oracle.} If ground truth data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation. This is realized by simply comparing the outcome of a correction using a defined measure. The oracle only accepts corrections which improve the automatic segmentation---others get
discarded. This is guided proofreading with a perfect user, and allows us to assess the upper limit of improvements.

@@

\paragraph{Forced choice setting.} We present a user with the choice to accept or reject a correction. All potential split errors are seen. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. Therefore, we only present merge errors that have a probability threshold higher than $1-p_t$.

@@

We integrate guided proofreading into an existing large data connectomics workflow. The web-based system is designed with a novice-friendly user interface (Fig.~\ref{fig:ui}). We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data. The user cannot to distinguish the current labeling from the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown.

### 2016-11-15 paper/related_work.tex

Recent papers have attacked the problem of proofreading massive datasets through crowdsourcing with novices~\cite{saalfeld09,anderson2011,Giuly2013DP2}. One popular platform is EyeWire, by Kim \etal~\cite{eyewire_nature}, where participants earn virtual rewards for merging over-segmented labelings to reconstruct retina cells.

@@

\paragraph{Computer-aided Proofreading.} Uzunbas \etal~\cite{uzunbas} showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This segmentation technique produces uncertainty estimates, which inform potential regions for proofreading to the user. While this applies to isotropic volumes, more work is needed to apply it to the typically anisotropic connectromics dataset volumes.

>>>>

Recent papers have tackled the problem of proofreading massive datasets through crowdsourcing with novices~\cite{saalfeld09,anderson2011,Giuly2013DP2}. One popular platform is EyeWire, by Kim \etal~\cite{eyewire_nature}, where participants earn virtual rewards for merging over-segmented labelings to reconstruct retina cells.

@@

\paragraph{Computer-aided Proofreading.} Uzunbas \etal~\cite{uzunbas} showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This segmentation technique produces uncertainty estimates, which inform potential regions for proofreading to the user. While this applies to isotropic volumes, more work is needed to apply it to the typically anisotropic connectomics dataset volumes.
